\index{BPatch_sourceObj: : : : : : :!}{

The BPatch_sourceObj class is the C++ superclass for the BPatch_function, BPatch_module, and BPatch_image classes.

It provides a set of common methods for all three classes. In addition, it can be used to build a “generic” source

navigator using the getObjParent and getSourceObj methods to get parents and children of a given level (i.e. the parent

of a module is an image, and the children will be the functions).}





\bigskip



{

enum BPatchErrorLevel\index{BPatchErrorLevel: : : : : : :!} { BPatchFatal, BPatchSerious, BPatchWarning, BPatchInfo

};}





\bigskip



{

enum BPatch_sourceType {



{

BPatch_sourceUnknown,



{

BPatch_sourceProgram,}



{

BPatch_sourceModule,



{

BPatch_sourceFunction,



{

BPatch_sourceOuterLoop,



{

BPatch_sourceLoop,



{

BPatch_sourceStatement };}





\bigskip



{

BPatch_sourceType getSrcType\index{getSrcType: : : : : : :!}()}



{

Returns the type of the current source object.





\bigskip



{

void getSourceObj\index{getSourceObj: : : : : : :!}(std::vector<BPatch_sourceObj *> &objs)}



{

Returns the child source objects of the current source object. For example, when called on a BPatch_sourceProgram

object this will return objects of type BPatch_sourceFunction. When called on a BPatch_sourceFunction object it may

return BPatch_sourceOuterLoop and BPatch_sourceStatement objects.}





\bigskip



{

BPatch_sourceObj *getObjParent\index{getObjParent: : : : : : :!}()}



{

Return the parent source object of the current source object. The parent of a BPatch_­image is NULL.}



{

typedef enum BPatch_language {}



{

BPatch_c,



{

BPatch_cPlusPlus,



{

BPatch_fortran,



{

BPatch_fortran77,



{

BPatch_fortran90,}



{

BPatch_f90_demangled_stabstr,



{

BPatch_fortran95,}



{

BPatch_assembly,



{

BPatch_mixed,



{

BPatch_hpf,



{

BPatch_java,



{

BPatch_unknownLanguage



{

} BPatch_language;}





\bigskip



{

BPatch_language getLanguage\index{getLanguage: : : : : : :!}()



{

Return the source language of the current BPatch_sourceObject. For programs that are written in more than one

language, BPatch_mixed will be returned. If there is insufficient information to determine the language,

BPatch_unknownLanguage will be returned.}



