\section[Appendix C {}- Common pitfalls]{Appendix C - Common pitfalls}
{
This appendix is designed to point out some common pitfalls that users have reported when using the Dyninst system.
Many of these are either due to limitations in the current implementations, or reflect design decisions that may not
produce the expected behavior from the system.}

{
Attach followed by detach}

{
If a mutator attaches to a mutatee, and immediately exits, the current behavior is that the mutatee is left suspended.
To make sure the application continues, call detach with the appropriate flags.}

{
Attaching to a program that has already been modified by Dyninst}

{
If a mutator attaches to a program that has already been modified by a previous mutator, a warning message will be
issued. We are working to fix this problem, but the correct semantics are still being specified. Currently, a message
is printed to indicate that this has been attempted, and the attach will fail.}

{
Dyninst is event-driven}

{
Dyninst must sometimes handle events that take place in the mutatee, for instance when a new shared library is loaded,
or when the mutatee executes a fork or exec. Dyninst handles events when it checks the status of the mutatee, so to
allow this the mutator should periodically call one of the functions BPatch::pollForStatusChange,
BPatch::wait­ForStatusChange, BPatch_thread::isStopped, or BPatch_­thread::is­Termin­ated.}

{
Missing or out-of-date DbgHelp DLL (Windows)}

{
Dyninst requires an up-to-date DbgHelp library on Windows. See the section on Windows-specific architectural
issues for details.}

{
Portland Compiler Group – missing debug symbols}

{
The Portland Group compiler (pgcc) on Linux produces debug symbols that are not read correctly by Dyninst. The
binaries produced by the compiler do not contain the source file information necessary for Dyninst to assign the debug
symbols to the correct module.}
