\section{Type System}

The Dyninst type system is based on the notion of structural equivalence. Structural equivalence was selected to allow

the system the greatest flexibility in allowing users to write mutators that work with applications compiled both with

and without debugging symbols enabled. Using the create* methods of the BPatch class, a mutator can construct type

definitions for existing mutatee structures. This information allows a mutator to read and write complex types even

if the application program has been compiled without debugging information. However, if the application has been

compiled with debugging information, Dyninst will verify the type compatibility of the operations performed by the

mutator.



{

The rules for type computability are that two types must be of the same storage class (i.e. arrays are only compatible

with other arrays) to be type compatible. For each storage class, the following additional requirements must be met

for two types to be compatible:}



{

Bpatch_dataScalar



{

Scalars are compatible if their names are the same (as defined by strcmp) and their sizes are the same.}



{

BPatch_dataPointer}



{

Pointers are compatible if the types they point to are compatible.}



{

BPatch_dataFunc



{

Functions are compatible if their return types are compatible, they have same number of parameters, and position by

position each element of the parameter list is type compatible.}



{

BPatch_dataArray



{

Arrays are compatible if they have the same number of elements (regardless of their lower and upper bounds) and the base

element types are type compatible.}



{

BPatch_dataEnumerated



{

Enumerated types are compatible if they have the same number of elements and the identifiers of the elements are the

same.}



{

BPatch_dataStructure}



{

BPatch_dataUnion}



{

Structures and unions are compatible if they have the same number of constituent parts (fields) and item by item each

field is type compatible with the corresponds field of the other type.}



{

In addition, if either of the types is the type BPatch_unknownType, then the two types are compatible. Variables in

mutatee programs that have not been compiled with debugging symbols (or in the symbols are in a format that the Dyninst

library does not recognize) will be of type BPatch_unknownType.}
